Multi-line Intensity Mapping

### 2019-04-11 paper/ms.tex
Add CO subsection and appendix

>>>>

\subsection{\CO{} Forecasts for CCAT-p and CONCERTO} \label{ssec:forecasts_tf}
Armed with some intuition from the simple white noise-dominated case, we now
turn to forecasting constraints that can be placed on the CO bias factors. Our
modelling of the \CO{} intensity as a function of redshift follows
\citet{2016ApJ...825..143L} and is outlined in Appendix~\ref{app:co_int}. We
assume that $b_i=3$ for each CO line.

\appendix
\section{CO Intensity Modelling} \label{app:co_int}
To model the statistical fluctuation and amplitude of the \CO{} intensity maps
we follow \citet{2016ApJ...825..143L}, and briefly summarize the procedure
here. We begin by assuming a Schechter form for the star formation rate
function,
\beq\label{eq:schechter}
\phi(\SFR)\,\text{d}\SFR = \phi_*
\left(\frac{\SFR}{\SFR_*}\right)^{\alpha}\exp{\left[-\frac{\SFR}{\SFR_*}\right]}
\frac{\text{d}\SFR}{\SFR_*}
\eeq
where $\alpha$ is the faint-end slope, $\SFR_*$ is the characteristic
star-formation rate, and $\phi_*$ is the characteristic number density. The
average specific intensity in a line $l$ can be related to the comoving
emissivity by \citep{2011ApJ...741...70L, 2013ApJ...768...15P},
\beq\label{eq:emiss_to_int}
\avg{I_l} = \frac{\epsilon_l}{4\pi \nu_{\text{rest},l}}\frac{c}{H(z)}\text{,}
\eeq
where $\nu_{\text{rest},l}$ is the rest-frame emission frequency and
$\epsilon_l$ is the comoving emissivity, each of line $l$. Assuming a linear
luminosity-SFR relation with a constant of proportionality of $L_0^l$, along
with the Schechter form for the SFR function (Equation~\ref{eq:schechter}), it
follows that \citep{2013ApJ...768...15P},
\beq\label{eq:com_emiss}
\epsilon_l = \phi_* L_0^{l}
\frac{\SFR_*}{1\,\Msun\text{yr}^{-1}}\Gamma{(2+\alpha)}\text{.}
\eeq
We adopt the value of $L_0^{\CO}$ for each line transition from
\citet{2010JCAP...11..016V}.
